---
title: "Common File"
author: "Louise & Esteban"
format: html
editor: visual
---

test


## Types and Classes

### Types

```{r}
typeof(1.5)
typeof("toto")
typeof('between single quotes')
typeof(TRUE)
typeof(1L)
typeof(1)
typeof(typeof)
typeof(list())
```

### Classes

```{r}
data(iris)
typeof(iris)
class(iris)
```


## Vectors

###Introduction 

Many things in R are vectors (and most of the other thinkgs are lists)

A vector is a collection of values of the same type (possibly a single value).

```{r}
x <- 15.25
length(x) # all vectors have a length
x[1]
```


THe c function can be seen as a creative function or, more accurately, as a vector concatenation function 

```{r}
y <- c(1, -2, 45, 1.5, -1e-10) # concatenation of multiple vectors (of 1 element)
y
typeof(y)
y[2]
length(y)
```
### Character vectors

```{r}
z <- "Alice"
length(z)
```


Salvation comes from 'stringr' package

```{r}
library(stringr)
```

```{r}
str_length(z)
```

```{r}
complicated <- 'â˜€ï¸ðŸ˜Ž'
complicated
length(complicated)
str_length(complicated)
```
```{r}
some_values <- c('â˜€ï¸ðŸ˜Ž')
some_values
length(some_values)
str_length(some_values)
```

### Indexing

```{r}
x <- c(6,5,1,2,3,4)
x[3]
```
```{r}
x
x[4] <- 4
x
```
```{r}
y<-x
y
```
Assignement can be understood as a value semanti assignment x and y are different vectors with the same initial content.
```{r}
x[1]<-18
x
y
```


Therefore, modifying x has no effect on y


Indexing is made with vectors of any length

```{r}
x
x[c(2,2,1,4,3,4)]
x
```
```{r}
x[c(-1)]
```


```{r}
y <- c('A','B','C')
y <- c(TRUE, FALSE, TRUE)
y
```


## Indexing

## Lists 

```{r}
broken <- c(1L, 1.5, "toto",FALSE)
broken
typeof(broken)
```

Vectors must  be type uniform, which will trigger a conversion to character in many cases. 

Lists do not have this limitation.

### Creating  a list

test conflict


